Models

### 2024-05-16 analysis/05_model_metrics.Rmd
Add min 10 years to sensitivity analysis

1. Min time series duration
```{r}
dur_dfs <- list(min3 = filter(model_data, duration > 2),
                min4 = filter(model_data, duration > 3),
                min5 = filter(model_data, duration > 4))

@@

min3_bad <- bad_dur_models %>% filter(dataID == "min3") %>% pull(metric)
min4_bad <- bad_dur_models %>% filter(dataID == "min4") %>% pull(metric)
min5_bad <- bad_dur_models %>% filter(dataID == "min5") %>% pull(metric)

refit_dur <- bind_rows(pmap_dfr(filter(mods, model_id == "base", metric_name %in% min3_bad), get_model, data = dur_dfs$min3, REML = FALSE) %>% mutate(dataID = "min3"),
                       pmap_dfr(filter(mods, model_id == "base", metric_name %in% min4_bad), get_model, data = dur_dfs$min4, REML = FALSE) %>% mutate(dataID = "min4"),
                       pmap_dfr(filter(mods, model_id == "base", metric_name %in% min5_bad), get_model, data = dur_dfs$min5, REML = FALSE) %>% mutate(dataID = "min5")
)

>>>>

1. Min time series duration
```{r}
dur_dfs <- list(min3 = filter(model_data, duration > 2),
                min4 = filter(model_data, duration > 3),
                min5 = filter(model_data, duration > 4),
                min10 = filter(model_data, duration > 9))

@@

min3_bad <- bad_dur_models %>% filter(dataID == "min3") %>% pull(metric)
min4_bad <- bad_dur_models %>% filter(dataID == "min4") %>% pull(metric)
min5_bad <- bad_dur_models %>% filter(dataID == "min5") %>% pull(metric)
min10_bad <- bad_dur_models %>% filter(dataID == "min10") %>% pull(metric)

refit_dur <- bind_rows(pmap_dfr(filter(mods, model_id == "base", metric_name %in% min3_bad), get_model, data = dur_dfs$min3, REML = FALSE) %>% mutate(dataID = "min3"),
                       pmap_dfr(filter(mods, model_id == "base", metric_name %in% min4_bad), get_model, data = dur_dfs$min4, REML = FALSE) %>% mutate(dataID = "min4"),
                       pmap_dfr(filter(mods, model_id == "base", metric_name %in% min5_bad), get_model, data = dur_dfs$min5, REML = FALSE) %>% mutate(dataID = "min5"),
                       pmap_dfr(filter(mods, model_id == "base", metric_name %in% min10_bad), get_model, data = dur_dfs$min10, REML = FALSE) %>% mutate(dataID = "min10")
)
